### 2017-04-11 paper/samplebody-journals.tex
added images and results sections to paper

\section{Next Steps}

>>>>

\section{Progress}

\quad Our most significant hurdle was in getting our data into a tool for some initial experimentation. While JSON formatting is extremely common in web applications, it seems that it's integration in data mining software has lagged. After several unsuccessful attempts to view our data through WEKA, we opted for a different tool, RapidMiner. From here, we've taken two routes: 1) running a python script to convert the JSON to CSV and 2) import the data into a local MongoDB instance and connect via the proper port. Both methods have finally allowed some degree of visualization to better direct our inquiry.

\section{Results}

\subsection{Businesses}

\quad After importing the CSV formatted version of the data we tested some basic visualization of the data. For instance, in Figure 1 we created a histogram of the average star for a business versus the state in which it?s located. Basic graphs like these help refine our question. For example, why does Illinois have significantly lower average stars than others?

\quad The most pervasive issue with our business data is that many entries are missing data, most notably the 'attributes' and address information. Since attributes are managed by the account owner, they vary widely across the businesses.

\begin{figure}
\includegraphics[width=0.75\textwidth, center]{b_rating_by_state}
\end{figure}

\subsection{Users}

\begin{figure}
\includegraphics[width=0.5\textwidth, center]{u_reviews_vs_stars}
\end{figure}

\quad
\section{Next Steps}
